### 2023-11-21 response_to_r1.md

# Response to reviewers of "Spreadsheet modeling and wrangling with Python"

I'd like to thank the reviewer and the editor for their thoughtful comments on this paper. I have
done by best to address them and to improve the paper.

@@

The publication by Alderson (2022) is very relevant and I'm not sure how I missed seeing that. I've integrated it into the paper and cited it. Thank you for bringing it to my attention.

> One particularly relevant example are the courses in computation offered by the Naval Postgraduate School and described in Alderson (2022). In their courses, Jupyter notebooks (discussed in more detail in the next section) play a prominent role in providing an interactive development and learning environment for Python within an operations research context.

In the first version I avoid citing my own work in ITE even though it is quite relevant. It now seems appropriate to add these and I have done
that in the section describing my speadsheet based analytics course.

@@

**Response 2**

I understand. I've added more explanation to the relevant paragraph. As opposed to adding a table or graphic that abstracts the details, I'm encouraging the readers to visit the relevant course landing pages as they include nicely structured topic outlines that make it very clear how EwP fits in to the Python material covered by our PCDA and AAP courses.

Here's the reworked paragraph:

> At our institution, The EwP module is part of a business course entitled  [Advanced Analytics with
Python](http://www.sba.oakland.edu/faculty/isken/courses/aap) (AAP). The students taking this course have already taken the PCDA course within where learned fundamental Python programming within the context of data analytics over seven weeks. The PCDA course ends with intro to the [scikit-learn library](https://scikit-learn.org/stable/index.html) for doing predictive modeling in Python and the AAP course begins where the PCDA course ends. The EwP module follows immediately after the modules on machine learning and builds on the Python fundamentals which were covered in the PCDA course. The EwP module could also be used as part of a semester long Python based analytics course in which the Python modules covered in the PCDA course are followed by more advanced topics such as EwP or other topics in our AAP course. The only reason the EwP module is not included in the PCDA course is that Python is only covered in half of that course - the other half being an introduction to R and Linux. If you visit the open access [PCDA course
website](http://www.sba.oakland.edu/faculty/isken/courses/pcda/)  and [AAP course
website](http://www.sba.oakland.edu/faculty/isken/courses/aap/), you can see the topic outline for each course and how the EwP module is positioned.

I'd like to stress that a big part of my paper is that it isn't just a paper. It is backed by a huge amount of public, freely available and Creative Commons licensed course websites and course content. Anyone who is interested in adapting my materials for their course is free to do so. Everything other than the homework assignments and quizzes are publicly accessible from the course websites. That's why throughout this paper I provide hyperlinks to relevant parts of the EwP course website or course content. This allows the reader to have a richer reading experience - instead of just a paper which necessarily is limited by what it can contain, the reader can view the entirety of the Jupyter notebooks, in html format, which make up the modules. ITE is an online journal and I'm trying to take advantage of the capabilities offered by such a platform.

@@

**Comment 3**

Are the students already familiar with the Jupyter notebook environment from their PCDA course, and therefore the instructor continues using the same environment, or are the students using a different development environment in their preceding course?

**Response 3**

Yes, we use Jupyter notebooks as well as a integrated development environment (either Spyder, PyCharm, or VSCode) in the PCDA course. The same tools are used in the AAP course. All of the technical and logistical details of both courses are described in excruciating detail in the public course websites linked to in the paper - see [Software and pcda virtual machine](http://www.sba.oakland.edu/faculty/isken/courses/pcda/pcda_vm.html) for the PCDA course and [Setting up your analytics machine](http://www.sba.oakland.edu/faculty/isken/courses/aap/setup_analytics_machine.html) for the AAP course.

@@

The same with source control – it is not clear to me why the program chose to include software engineering related discussion about source control in the EwP module of the AAP course, could the author please add a bit of discussion around that?

**Response 4**

I didn't choose that. Version control is covered in the very first module of the AAP course and students use git and GitHub for the ML module that precedes the EwP module. The following sentence is in the original version of the paper:

> Students are reminded of the importance of version control and we initialize a git repository for our budding package. The basics of version control were already covered in the first week of the course.

@@

Again, the AAP course website main page at [http://www.sba.oakland.edu/faculty/isken/courses/aap/](http://www.sba.oakland.edu/faculty/isken/courses/aap/) contains a detailed topic outline and the reader can see what is covered when.

The reason that we dive deeper into version control and project folder structure at this point is because we are now trying to create a deployable Python package containing the work we did in the previous three notebooks. These things matter in software development and we want to emphasize their importance to the students.

@@

**Response 1**

I'm definitely not trying to offer EwP as an alternative to Excel. I've taught an Excel based spreadsheet modeling course for over 20 years and have used Excel extensively in both industry as well as in academic settings. I love spreadsheets and have for a long time. But, they do
have their limitations and the better our students are at assessing when a spreadsheet is and is not appropriate, the better off they will be. This is not some novel argument. Excel bashing is rampant in corporate IT and analytics settings. Quite honestly, even Jupyter notebooks have major shortcomings when it comes to productionizing analytical models implemented in Python and I mention this in the paper - and that's why I also make students use an actual IDE to write code in addition to the things we do in notebooks. There's a lot of nuance in knowing how to effectively wield tools like Excel and Python in professional analytics environments. This is a big part of the motivation behind the development of my courses and in writing this paper.

My intent is to provide an interesting way for business students to learn more advanced Python concepts through a very familiar lens of spreadsheet modeling. In addition, I want to expose them to the abilities of Python in automating manipulation of spreadsheets. Now with MS announcing the inclusion of Python within Excel, the complementary nature of these two powerhouse tools will become even more important. To that end, I've modified the beginning of that paragraph as follows:

> Despite numerous calls for, and predictions of, the eradication of spreadsheets from the business world, Excel and other spreadsheets are \href{https://benn.substack.com/p/the-next-billion-programmers}{alive and well}. Their flexibility is unparalleled and it is unrealistic to expect them to disappear anytime soon. If anything, the [recent announcement by Microsoft](https://techcommunity.microsoft.com/t5/excel-blog/announcing-python-in-excel-combining-the-power-of-python-and-the/ba-p/3893439)
 that users will be able combine Python scripts with Excel formulas within the same workbook, will likely solidify Excel's place in the analytics space.

@@

**Response 2**

I wrestled with this when writing the paper. Instead of including more figures, I opted, as I described above, to include prominent hyperlinks to HTML versions of the notebooks in the relevant section headers.

For example:

> 3.3. Notebook 3: Monte-Carlo simulation ([html version](http://www.sba.oakland.edu/faculty/isken/excel_with_python/what_if_3_simulation.html))

@@

I also added explicit language early in the paper that highlighted these hyperlinks and encouraged readers to use them.

> While all of the notebooks are publicly available (see Section 6), links to html versions of
each of the notebooks are provided throughout the document and readers are encouraged to use
them while reading to see exactly how each topic is presented.

My intent is for the reader to open the html versions of the notebooks in a browser tab and then they can see the entire notebook. Code snippets taken out of context are not nearly as useful as following the narrative flow of the notebook - this is the real strength of Jupyter notebooks for teaching.

If the reviewer and editor want me to add more code screenshots, I can, but I'd really prefer readers look at the (html versions of) the actual notebooks. Of course, the actual Jupyter notebooks are also available from the course website.

@@

**Comment 3**

In section 7, the author(s) need to more fully address the roll out of Python in
Excel. Does this alter their pedagogy? It may not if the focus is develop the skills
outlined in the Introduction and listed below
o  teaching relevant and more advanced Python to business students using familiar and
simple modeling examples,  conveying a sense of the software design and development
process,  acting as a tour guide for a learning journey,  teaching students to think and
act like a software developer, not just an analyst
In any case, I think the paper needs a more comprehensive discussion regarding
this development.

**Response 3**

I've added reference to this development in the opening section as I mentioned in Response 1 above. I've also made the last section all about the future which opens with this expanded paragraph.

> Rumors have swirled for a number of years that Microsoft was considering adding Python as a first class language alternative to VBA within their MS Office suite of packages \cite{cimpanuMicrosoftConsidersAdding2017}. During the review process for this article, this development [finally
materialized](https://techcommunity.microsoft.com/t5/excel-blog/announcing-python-in-excel-combining-the-power-of-python-and-the/ba-p/3893439)
, albeit in a limited roll out to beta testers. This has potentially enormous implications for the future of both Excel and Python. At this point, it is probably safe to say that this development further underscores the importance of business analytics students adding Python to their analytical toolbox.

### 2023-11-21 python_excel_ite_r1.tex
finished revisions and response to reviewers

Spreadsheet based modeling has transformed the teaching of management science in business schools over the past twenty plus years. The late 1990's saw first editions of game changing textbooks \citep{winstonPracticalManagementScience2018,ragsdaleSpreadsheetModelingDecision2017} focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education (ITE) journal \citep{baker2000:lp,bell2000:statistics,evans2000:simulation,carraway2000:mba,ragsdale2001:teaching,savage2001:blitzograms}. The next few decades saw numerous textbooks, including {\citet{powellBusinessAnalyticsArt2019, camm2020business}}, and teaching papers in journals such as \href{https://pubsonline.informs.org/journal/ited}{ITE} that prominently featured spreadsheet based modeling.

@@

The PCDA course, like many introductory data science courses, focuses mostly on data wrangling, exploratory data analysis (EDA), and statistical/machine learning based predictive models. In teaching EDA using tools like ggplot2, students are challenged to think about how they would go about trying to use Excel to create some of the plots that are easy to do with R and Python based plotting libraries. There is some limited coverage of using Python to open Excel files and do worksheet manipulation. However, other than a Python based simulation of the Monte Hall 3-door problem, there was no real attempt to do the kind of modeling that is the focus of most spreadsheet based modeling textbooks.

@@

At our institution, The EwP module is part of a business course entitled  \href{http://www.sba.oakland.edu/faculty/isken/courses/aap}{Advanced Analytics with Python} (AAP). The students taking this course have already taken the PCDA course within which they learned fundamental Python programming within the context of data analytics over seven weeks. The PCDA course ends with intro to the \href{https://scikit-learn.org/stable/index.html}{scikit-learn library} for doing predictive modeling in Python and the AAP course begins where the PCDA course ends. The EwP module follows immediately after the modules on machine learning and builds on the Python fundamentals which were covered in the PCDA course. The EwP module could also be used as part of a semester long Python based analytics course in which the Python modules covered in the PCDA course are followed by more advanced topics such as EwP or other topics in our AAP course. The only reason the EwP module is not included in the PCDA course is that Python is only covered in half of that course - the other half being an introduction to R and Linux. If you visit the open access \href{http://www.sba.oakland.edu/faculty/isken/courses/pcda/}{PCDA course website}  and \href{http://www.sba.oakland.edu/faculty/isken/courses/aap/}{AAP course website}, you can see the topic outline for each course and how the EwP module is positioned.

@@

\begin{itemize}
	\item familiarity with Jupyter notebooks and an integrated development environment such as \href{https://www.spyder-ide.org/}{Spyder}, \href{https://code.visualstudio.com/}{VSCode} or \href{https://www.jetbrains.com/pycharm/}{PyCharm},
	\item variables, arithmetic and boolean operators, basic data types,
	\item data structures such as lists, dictionaries, tuples, NumPy arrays and pandas dataframes,
	\item flow control such as branching with \texttt{if \ldots else} and iterating with \texttt{for} and \texttt{while}
	\item module imports,
	\item using built in functions and accessing methods and properties of objects,
	\item creating functions,
	\item basic use of NumPy and pandas for data wrangling and analysis,
	\item basic plotting with matplotlib.
\end{itemize}

@@

All of the Python modules in the PCDA course as well as the entire AAP course are taught using a combination of Jupyter notebooks, Python scripts, and videos that walk readers through the notebooks. Jupyter notebooks, part of \href{https://jupyter.org/}{Project Jupyter}, are an example of \textit{literate computing} \citep{perez2015project} and allow one to create rich interactive documents that support iterative exploration and development.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[scale=0.5]{cells_edit_mode}
\caption{Notebook cells in edit model}
\label{fig:cells_edit_mode}
\end{figure*}

@@

There are two overarching learning objectives for this \href{http://www.sba.oakland.edu/faculty/isken/courses/aap/mod3a_whatif.html}{first EwP submodule} - see Figure \ref{fig:objectives_whatif} for how the objectives are presented to students via the course website. Students learn how Python might be used to do something they are quite familiar with doing in a spreadsheet -- model building and sensitivity analysis. At the same time, they encounter more advanced Python programming concepts and techniques. In this way, the computational problem to be solved drives the introduction of more advanced Python concepts and techniques instead of such things being presented in a vacuum. I make it a point to show that there are often multiple possible approaches to a computational problem by being willing to abandon one approach and trying another. Emphasis is given to the lessons learned from each path explored. Every notebook is accompanied by screencasts that walk the students through the material and act as a guided tour with challenges to overcome along the way. While all of the notebooks are publicly available (see Section \ref{sec:software}), links to html versions of each of the notebooks are provided throughout the document and readers are encouraged to use them while reading to see exactly how each topic is presented.

@@

A few design dilemmas are posed and some non-working approaches illustrated as we try to decide on how to implement an n-way data table function for this new object oriented model. These meta reflections are intentionally included to better mimic actual software development and reinforce the idea that software development is much more than simply writing code to implement a perfectly thought out design. We forge ahead with some preliminary ideas and are confronted with an intermediate problem related to generating a list of dictionaries that represent combinations of inputs, or \textit{scenarios}, to evaluate. This provides a great opportunity to remind students of one of the great strengths of the open source software ecosystem -- we can leverage work done in other packages and even look at actual source code to see how something was implemented. In this case, the well known \href{https://scikit-learn.org/stable/}{scikit-learn} package (\cite{scikit-learn}) has a \code{ParameterGrid} function that solves our scenario generation problem quite nicely. This example also reminds the students of the value of being able to make sense of API documentation and to understand object oriented code written by others.

@@

Key software design changes are then made which will make the code easier to use. These changes include creating an abstract \code{Model} base class from which different model classes can be created and moving the \code{data\_table}, \code{goal\_seek}, and \code{simulate} functions into the \code{Model} base class as methods. All of the code is moved into a code module named \code{whatif.py}. Students are now ready to learn about the basics of turning our code into an installable package. This requires a basic understanding of two key Python files that are ubiquitous in Python pacakges - \code{\_\_init\_\_.py} and \code{setup.py}. Options are presented for installing our package locally so that we can use it for different modeling projects. This includes an explanation of how and where Python searches for packages when \code{import} statements are encountered in code. There is much complexity lurking here and students are reminded that they will need to revisit this topic frequently. I have made every effort to distill things down to a minimal level of complexity needed to convey the important points.

@@

The deployment focused submodule ends with a short notebook discussing the different types of documentation needed in a typical project. This includes code comments, \href{https://peps.python.org/pep-0257/}{docstrings}, \code{readme} files and generating documentation by creating \href{https://www.sphinx-doc.org/en/master/usage/restructuredtext/basics.html}{reStructuredText} files (similar to but more powerful than markdown) and using \href{https://www.sphinx-doc.org/en/master/index.html}{Sphinx}, the Python documentation generation tool. This is one of those tasks that few people like to do but can be very important for the long term success of a project. Even if you are just creating a tool for yourself, you will forget the details over time and documentation can be very beneficial in refreshing your memory.

@@

While this first example is not necessarily Excel related, using Excel to consolidate csv files through a series of manual Copy-Paste operations is something that many Excel users will admit to having done. After getting familiar with pathlib, a library for working with file systems which has recently been added to Python's standard library, students are led through the development of a short procedure that creates a list of the csv files to concatenate and then uses pandas to read and combine the files in a \code{DataFrame} and writes out the consolidated data as a csv file.

@@

\section{Software availability}
\label{sec:software}

@@

\section{Classroom experience and the future}
\label{sec:classroom}

@@

Rumors have swirled for a number of years that Microsoft was considering adding Python as a first class language alternative to VBA within their MS Office suite of packages \cite{cimpanuMicrosoftConsidersAdding2017}. During the review process for this article, this development \href{https://techcommunity.microsoft.com/t5/excel-blog/announcing-python-in-excel-combining-the-power-of-python-and-the/ba-p/3893439}{finally materialized}, albeit in a limited roll out to beta testers. This has potentially enormous implications for the future of both Excel and Python. At this point, it is probably safe to say that this development further underscores the importance of business analytics students adding Python to their set of analytical toolbox. There continues to be significant interest in using Python to manipulate not only Excel workbooks but other office documents such as Powerpoint presentations \citep{cannyPythonpptx2013}. Given that the ubiquity of both Excel and Powerpoint in business education and practice, inclusion of this material in a business school Python based analytics course seems quite appropriate. Students can learn more advanced and extremely useful Python concepts and techniques within a context with which they are intimately familiar. Manipulation of MS Office documents is directly relevant to the job content of many of our students. This teaching module is a natural complement to the commonly taught spreadsheet based analytics and introductory data science courses found in many business schools and provides an interesting way to teach and learn Python for analytics.

>>>>

Spreadsheet based modeling has transformed the teaching of management science in business schools over the past twenty plus years. The late 1990s saw first editions of game changing textbooks \citep{winstonPracticalManagementScience2018,ragsdaleSpreadsheetModelingDecision2017} focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education (ITE) journal \citep{baker2000:lp,bell2000:statistics,evans2000:simulation,carraway2000:mba,ragsdale2001:teaching,savage2001:blitzograms}. The next few decades saw numerous textbooks, including {\citet{powellBusinessAnalyticsArt2019, camm2020business}}, and teaching papers in journals such as \href{https://pubsonline.informs.org/journal/ited}{ITE} that prominently featured spreadsheet based modeling.

@@

The PCDA course, like many introductory data science courses, focuses mostly on data wrangling, exploratory data analysis (EDA), and statistical/machine learning based predictive models. In teaching EDA using tools like [ggplot2](https://ggplot2.tidyverse.org/), students are challenged to think about how they would go about trying to use Excel to create some of the plots that are easy to do with R and Python based plotting libraries. There is some limited coverage of using Python to open Excel files and do worksheet manipulation. However, other than a Python based simulation of the Monte Hall 3-door problem, there was no real attempt to do the kind of modeling that is the focus of most spreadsheet based modeling textbooks.

@@

At our institution, The EwP module is part of a business course entitled  \href{http://www.sba.oakland.edu/faculty/isken/courses/aap}{Advanced Analytics with Python} (AAP). The students taking this course have already taken the PCDA course where they learned fundamental Python programming within the context of data analytics over seven weeks. The PCDA course ends with intro to the \href{https://scikit-learn.org/stable/index.html}{scikit-learn library} for doing predictive modeling in Python and the AAP course begins where the PCDA course ends. The EwP module follows immediately after the modules on machine learning and builds on the Python fundamentals which were covered in the PCDA course. The EwP module could also be used as part of a semester long Python based analytics course in which the Python modules covered in the PCDA course are followed by more advanced topics such as EwP or other topics in our AAP course. The only reason the EwP module is not included in the PCDA course is that Python is only covered in half of that course - the other half being an introduction to R and Linux. If you visit the open access \href{http://www.sba.oakland.edu/faculty/isken/courses/pcda/}{PCDA course website}  and \href{http://www.sba.oakland.edu/faculty/isken/courses/aap/}{AAP course website}, you can see the topic outline for each course and how the EwP module is positioned.

@@

\begin{itemize}
	\item variables, arithmetic and boolean operators, basic data types,
	\item data structures such as lists, dictionaries, tuples, NumPy arrays and pandas dataframes,
	\item flow control such as branching with \texttt{if \ldots else} and iterating with \texttt{for} and \texttt{while}
	\item module imports,
	\item using built in functions and accessing methods and properties of objects,
	\item creating functions,
	\item basic use of NumPy and pandas for data wrangling and analysis,
	\item basic plotting with matplotlib,
	\item familiarity with Jupyter notebooks and an integrated development environment such as \href{https://www.spyder-ide.org/}{Spyder}, \href{https://code.visualstudio.com/}{VSCode} or \href{https://www.jetbrains.com/pycharm/}{PyCharm}.
\end{itemize}

@@

All of the Python modules in the PCDA course as well as the entire AAP course are taught using a combination of Jupyter notebooks, Python scripts, and videos that walk readers through the notebooks. Jupyter notebooks, part of \href{https://jupyter.org/}{Project Jupyter}, are an example of \textit{literate computing} \citep{perez2015project} and allow the creation of rich interactive documents that support iterative exploration and development.

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[scale=0.5]{cells_edit_mode}
\caption{Notebook cells in edit mode}
\label{fig:cells_edit_mode}
\end{figure*}

@@

There are two overarching learning objectives for this \href{http://www.sba.oakland.edu/faculty/isken/courses/aap/mod3a_whatif.html}{first EwP submodule}. Students learn how Python might be used to do something they are quite familiar with doing in a spreadsheet -- model building and sensitivity analysis. At the same time, they encounter more advanced Python programming concepts and techniques. In this way, the computational problem to be solved drives the introduction of more advanced Python concepts and techniques instead of such things being presented in a vacuum. See Figure \ref{fig:objectives_whatif} for how the objectives are presented to students via the course website.

I make it a point to show that there are often multiple possible approaches to a computational problem by being willing to abandon one approach and trying another. Emphasis is given to the lessons learned from each path explored. Every notebook is accompanied by screencasts that walk the students through the material and act as a guided tour with challenges to overcome along the way. While all of the notebooks are publicly available (see Section \ref{sec:software}), links to html versions of each of the notebooks are provided throughout the document and readers are encouraged to use them while reading to see exactly how each topic is presented.

@@

A few design dilemmas are posed and some non-working approaches illustrated as we try to decide on how to implement an n-way data table function for this new object oriented model. These meta reflections are intentionally included to better mimic actual software development and reinforce the idea that software development is much more than simply writing code to implement a perfectly thought out design. We forge ahead with some preliminary ideas and are confronted with an intermediate problem related to generating a list of dictionaries that represent combinations of inputs, or \textit{scenarios}, to evaluate. This provides a great opportunity to remind students of one of the great strengths of the open source software ecosystem -- we can leverage work done in other packages and even look at actual source code to see how something was implemented. In this case, the well known \href{https://scikit-learn.org/stable/}{scikit-learn} package \citep{scikit-learn} has a \code{ParameterGrid} function that solves our scenario generation problem quite nicely. This example also reminds the students of the value of being able to make sense of API documentation and to understand object oriented code written by others.

@@

Key software design changes are then made which will make the code easier to use. These changes include creating an abstract \code{Model} base class from which different model classes can be created and moving the \code{data\_table}, \code{goal\_seek}, and \code{simulate} functions into the \code{Model} base class as methods. All of the code is moved into a code module named \code{whatif.py}. Students are now ready to learn about the basics of turning our code into an installable package. Options are presented for installing our package locally so that we can use it for different modeling projects. This includes an explanation of how and where Python searches for packages when \code{import} statements are encountered in code. There is much complexity lurking here and students are reminded that they will need to revisit this topic frequently. I have made every effort to distill things down to a minimal level of complexity needed to convey the important points.

@@

The deployment focused submodule ends with a short notebook discussing the different types of documentation needed in a typical project. This includes code comments, \href{https://peps.python.org/pep-0257/}{docstrings}, \code{readme} files and generating documentation by creating \href{https://www.sphinx-doc.org/en/master/usage/restructuredtext/basics.html}{reStructuredText} files (similar to, but more powerful than markdown) and using \href{https://www.sphinx-doc.org/en/master/index.html}{Sphinx}, the Python documentation generation tool. This is one of those tasks that few people like to do but can be very important for the long term success of a project. Even if you are just creating a tool for yourself, you will forget the details over time and documentation can be very beneficial in refreshing your memory.

@@

While this first example is not necessarily Excel related, using Excel to consolidate csv files through a series of manual Copy-Paste operations is something that many Excel users will admit to having done. After getting familiar with \code{pathlib}, a library for working with file systems which has recently been added to Python's standard library, students are led through the development of a short procedure that creates a list of the csv files to concatenate and then uses pandas to read and combine the files in a \code{DataFrame} and writes out the consolidated data as a csv file.

@@

\section{Software availability and classroom use}
\label{sec:software}

@@

@@

\section{The future of Python and Excel}
\label{sec:future}

Rumors have swirled for a number of years that Microsoft was considering adding Python as a first class language alternative to VBA within their MS Office suite of packages \cite{cimpanuMicrosoftConsidersAdding2017}. During the review process for this article, this development \href{https://techcommunity.microsoft.com/t5/excel-blog/announcing-python-in-excel-combining-the-power-of-python-and-the/ba-p/3893439}{finally materialized}, albeit in a limited roll out to beta testers. This has potentially enormous implications for the future of both Excel and Python. At this point, it is probably safe to say that this development further underscores the importance of business analytics students adding Python to their analytical toolbox.

There continues to be significant interest in using Python to manipulate not only Excel workbooks but other office documents such as Powerpoint presentations \citep{cannyPythonpptx2013}. Given that the ubiquity of both Excel and Powerpoint in business education and practice, inclusion of this material in a business school Python based analytics course seems quite appropriate. Students can learn more advanced and extremely useful Python concepts and techniques within a context with which they are intimately familiar. Manipulation of MS Office documents is directly relevant to the job content of many of our students. This teaching module is a natural complement to the commonly taught spreadsheet based analytics and introductory data science courses found in many business schools and provides an interesting way to teach and learn Python for analytics.
